### 2017-10-14 Gruba/10-appendix.tex

In this section, we show the results of our demo system for User Clustering. We carefully analyzed the statistical information of four groups obtained from user clustering.

@@

\stab(2) The users of group two are mostly female (as shown in Sub-Fig. \ref{fig:subfig2:fig21}) and are also mainly in Beijing (北京) (shown as Sub-Fig. \ref{fig:subfig2:fig22}). Similar as group one, most of them have number of followees close to followers (as shown in Sub-Fig. \ref{fig:subfig2:fig24}). The most active time of this group is mainly between 10 pm and 12 pm (as shown in Sub-Fig. \ref{fig:subfig2:fig25} and \ref{fig:subfig2:fig26}).

>>>>

In this section, we show the results of our system \sys{} for User Clustering. We carefully analyzed the statistical information of four groups obtained from user clustering.

@@

\stab(2) The users of group two are mostly female (as shown in Sub-Fig. \ref{fig:subfig2:fig21}) and are also mainly in Beijing (北京) (shown as Sub-Fig. \ref{fig:subfig2:fig22}). Similar as group one, most of them have followees close to followers (as shown in Sub-Fig. \ref{fig:subfig2:fig24}). The most active time of this group is mainly between 10 pm and 12 pm (as shown in Sub-Fig. \ref{fig:subfig2:fig25} and \ref{fig:subfig2:fig26}).
